A Data-Driven Framework for Neural Field Modelling

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to results, sigmoid parameters bit

Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied. For Part a), the kernel estimates are not in good accordance with the true kernel, as the true kernel falls outside of the confidence intervals in some areas. \dean{This is because???} 
\parham{this bit should change as well:} 
The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel. The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).

\subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}

\subsubsection{Results for Varying the Sensor Kernel Width}

>>>>

Parts a), b) and c) of Figure~\ref{fig:Figure8} show results from the Mexican hat kernel parameters were varied. For Part a), the kernel estimates are not in good accordance with the true kernel, as the true kernel falls outside of the confidence intervals in some areas. \dean{This is because??? the amplitude the central kernel is low, so noise has a greater effect (although this should just cause a wider confidence interval)?, the amplitude or the outer basis function is high (and the field is too small (boundary issues))? the spatial discretisation stuffs it up (the peaks of the extrema of the continuous kernel do not fall as discrete space locations)?}

\parham{this bit should change as well:} 
For parts b) and c) the figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel. The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(c).

\subsubsection{Results for Varying the Parameters of the Sigmoidal Activation Function}
To illustrate the effect of varying the 
Figure~\ref{fig:Figure11} shows a Hinton diagram demonstrating the estimation accuracy for the connectivity kernel for various parameters of the sigmoid. 
\subsubsection{Results for Varying the Sensor Kernel Width}
